---
title: "Temperature dependence of biomass and ecosystem function depend on species interactions. Supplementary File 2: Phytoplankton and oxygen flux results in main text."
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r, echo=FALSE}
### 1. Load libraries and data
### load libraries
library(MuMIn)
library(nlme)
library(plyr)
library(tidyverse) 
library(broom)
library(reshape2)
library(lubridate)
library(hms)
library(zoo)
library(knitr)
library(gridExtra)
library(captioner)
```

```{r load data}
### load data
data <- read.csv("../data/GarzkedataA.csv")
alldata <- read.csv("../data/GarzkeAllwks.csv")
k <- 8.617342*10^-5  # eV/K
labels <- c(P = "Algae", PZ = "Algae + Grazers", PZN = "Algae + Grazers + Predators")
```

```{r captions, echo = FALSE}
table_nums <- captioner::captioner(prefix = "Table S2.") #sets prefix for all tables
table_nums(name = "Table_S2.1", caption = "Model selection results for Phytoplankton (Chl a) for linear mixed effects model", display = FALSE)
table_nums(name = "Table_S2.2", caption = "Parameter estimates from model PB8 (Table S2.1) for Phytoplankton (Chl a) for linear mixed effects model", display = FALSE)
table_nums(name = "Table_S2.3", caption = "Model selection results for Net Ecosystem Oxygen Production, with 1|Tank as a random effect. Model terms are: intercept (Int), trophic treatment (TL), Temperature - weekly average (Tw), temperature - expt average (Tt), interaction terms and statistical estimates", display = FALSE)
table_nums(name = "Table_S2.4", caption = "Parameter estimates from model NPP8 (Table S2.3) for Net Ecosystem Oxygen Productivity (NEP) for linear mixed effects model(For MS Figure 3)", display = FALSE)
table_nums(name = "Table_S2.5", caption = "Model selection results for Net Ecosystem Respiration, with 1|Tank as a random effect. Model terms are: intercept (Int), trophic treatment (TL), Temperature - weekly average (Tw), temperature - expt average (Tt), interaction terms and statistical estimates", display = FALSE)
table_nums(name = "Table_S2.6", caption = "Confidence intervals for model ER7 (Table S2.5) (For MS Figure 3", display = FALSE)

fig_nums <- captioner::captioner(prefix = "Figure S2.")
fig_nums(name = "Fig_S2.01", caption = "Chlorophyll a concentration over time", display = FALSE)
fig_nums(name = "Fig_S2.1", caption = "Chlorophyll a concentration", display = FALSE)
fig_nums(name = "Fig_S2.2", caption = "Trophic Treatment Effects on Chlorophyll a, Net Oxygen Ecosystem Production (NEP), and Net Ecosystem Respiration (ER)", display = FALSE)
fig_nums(name = "Fig_S2.3", caption = "Manuscript figure 3: Effects of temperature on oxygen flux and phytoplankton standing stock", display = FALSE)
```

## 0.5. Temporal Results 

```{r, echo = FALSE, Fig_S2.01,fig.width=5, fig.height=3}
Chl.time <- ggplot(data = alldata, aes(x = week, y = log(chla), ymin = 0)) +
  theme_bw() +
  theme(legend.position = "none") +
  geom_point() +
  theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank(),  
        legend.text = element_text(size=6), 
        legend.title = element_text(size = 7), 
        strip.background = element_blank()) +
  ylab("Phytoplankton Abundance \n ln(ug Chl a / L)")

Chl.time

CT1 <- lme(I(log(chla)) ~ week, random = ~ 1 | Tank, data=data, method="ML", na.action=na.omit) 
```

```{r, echo = FALSE, Fig_S2.02, fig.width=5, fig.height=3}
Chl.temp <- ggplot(data = alldata, aes(x = temp.wk, y = log(chla), ymin = 0)) +
  theme_bw() +
  theme(legend.position = "none") +
  geom_point() +
  theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank(),  
        legend.text = element_text(size=6), 
        legend.title = element_text(size = 7), 
        strip.background = element_blank()) +
  ylab("Phytoplankton Abundance \n ln(ug Chl a / L)")

Chl.temp

CT2 <- lme(I(log(chla)) ~ temp.wk, random = ~ 1 | Tank, data=data, method="ML", na.action=na.omit) 

```

## 1. Trophic Cascade Results (Figure 2 Main text)
### Calculate strength of grazing and strength of the trophic cascade on chla
```{r, echo = FALSE, Fig_S2.03, fig.width=3, fig.height=3}
#estimate mean temp for each power level
#alldata$week <- factor(alldata$week)
#alldata$power <- factor(alldata$power)

temps.pwr <- alldata %>%
  group_by(week, power) %>%
  dplyr::summarize(avgTemp = mean(average.temp, na.rm = TRUE))
View(temps.pwr)

TCchla <- as.tibble(alldata) %>%
group_by(week) %>%
select(., week, power, trophic.level, chla) %>%
spread(., trophic.level, chla) %>%
left_join(., temps.pwr, by = c("week", "power")) %>%
mutate(., invTavg = 1/((avgTemp + 273)*k)) %>%
mutate(., TC = log(PZN/PZ)) 

data <- TCchla

hist(TCchla$TC)
```

```{r, echo = FALSE, Fig_S2.04, fig.width=5, fig.height=3}
TC <- ggplot(data = TCchla, aes(x = invTavg, y = TC, ymin = 0)) +
  theme_bw() +
  #theme(legend.position = "none") +
  theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank(),  
        legend.text=element_text(size=6), 
        legend.title = element_text(size = 7), 
        legend.key = element_rect(fill = NA), 
        strip.background = element_blank()) +
  theme(strip.background = element_rect(colour="white", fill="white")) +
  geom_point(aes(group = week, color = as.factor(week)), size = 2) 

TC
```

```{r, echo = FALSE}
## power constitutes the group here, and we have 8 observations for each 'power'; however, our question is about whether the effect of temperature varies by week. that's why i want the week to be the group; but that goes against how we need to model the variance, grouped among the units (= 'power' levels) that are repeatedly sampled. SO, look for examples of aging subjects for repeated measures. we are looking here at an across-subject effect of interst, and we want to know whether it changes with subject age. 
data$power <- as.factor(data$power)
data$week <- as.numeric(data$week)

## let's model just week 9
TCmod9 <- lm(TC ~ invTavg, data=TCchla[TCchla$week == '9',], method="ML", na.action=na.omit)

TCmod8 <- lm(TC ~ invTavg, data=TCchla[TCchla$week == '8',], method="ML", na.action=na.omit)

TCmod7 <- lm(TC ~ invTavg, data=TCchla[TCchla$week == '7',], method="ML", na.action=na.omit)

TCmod6 <- lm(TC ~ invTavg, data=TCchla[TCchla$week == '6',], method="ML", na.action=na.omit)

TCmod5 <- lm(TC ~ invTavg, data=TCchla[TCchla$week == '5',], method="ML", na.action=na.omit)

TCmod4 <- lm(TC ~ invTavg, data=TCchla[TCchla$week == '4',], method="ML", na.action=na.omit)

TCmod3 <- lm(TC ~ invTavg, data=TCchla[TCchla$week == '3',], method="ML", na.action=na.omit)

TCmod2 <- lm(TC ~ invTavg, data=TCchla[TCchla$week == '2',], method="ML", na.action=na.omit)

## so this could work: 
TCmoda <- lme(TC ~ 1 + invTavg*week, random = ~ 1 + invTavg|power, data=TCchla, method="REML", na.action=na.omit)

#promising - high correlations so centre on T again?
TCmodJ <- lme(TC ~ invTavg*week, random = ~ 1|power + invTavg|week, data=TCchla, method="REML", na.action=na.omit)

TCmodb <- lme(TC ~ 1 + invTavg*week, random = ~ 1 + 1|power, data=TCchla, method="REML", na.action=na.omit)
TCmodc <- lme(TC ~ 1 + invTavg + week, random = ~ 1 + invTavg|power, data=TCchla, method="REML", na.action=na.omit)
TCres <- data.frame(model.sel(TCmoda, TCmodb, TCmodc))

```

`r table_nums("Table_S2.0")`

```{r Table_S2.1}
kable(TCmod, digits=2, col.names = c('Int','TL','Tw','Tt', 'Tw*Tt', 'Tw*TL','Tt*TL', 'df', 'logLik','AICc','d','w'))
```

### Calculate strength of grazing and strength of the trophic cascade on NPP2
```{r, echo = FALSE, Fig_S2.05, fig.width=3, fig.height=3}
#estimate mean temp for each power level
alldata$week <- factor(alldata$week)
alldata$power <- factor(alldata$power)

TCNPP <- as.tibble(alldata) %>%
group_by(week) %>%
select(., week, power, trophic.level, NPP2) %>%
spread(., trophic.level, NPP2) %>%
left_join(., temps.pwr, by = c("week", "power")) %>%
mutate(., TC = log(PZN/PZ)) 

hist(TCNPP$TC)
```

```{r, Fig_S2.06, fig.width=3, fig.height=3}

TCNPP <- ggplot(data = TCNPP, aes(x = avgTemp, y = TC, ymin = 0)) +
  theme_bw() +
  theme(legend.position = "none") +
  theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank(),  
        legend.text=element_text(size=6), 
        legend.title = element_text(size = 7), 
        legend.key = element_rect(fill = NA), 
        strip.background = element_blank()) +
  theme(strip.background = element_rect(colour="white", fill="white")) +
  geom_point(aes(group = week, shape = as.factor(week)), size = 2) 

TCNPP
```





### 2.1 Phytoplankton abundance (for Figure 3, Table 2 main text)

`r fig_nums("Fig_S2.1")`

```{r, Fig_S2.1,fig.width=3, fig.height=3}
hist(data$chla)
hist(log(data$chla))
```

## 2.1.1 Phytoplankton abundance candidate models
```{r, echo=FALSE}
#### Phytoplankton coefficients for Figure 2
data <- alldata
modPBF <- lme(log(chla) ~ 1 + I(invTi - invTT) + trophic.level + trophic.level*I(invTi - invTT) + I(invTT - mean(invTT)) + I(invTi - invTT)*I(invTT - mean(invTT)), random = ~ 1 | Tank, data=data, method="ML", na.action=na.omit) 
modPB8 <- lme(log(chla) ~ 1 + trophic.level*I(invTi - invTT) + trophic.level*I(invTT - mean(invTT)), random = ~ 1 | Tank, data=data, method="ML", na.action=na.omit)
modPB7 <- lme(log(chla) ~ 1 + I(invTi - invTT) + trophic.level + trophic.level*I(invTT - mean(invTT)), random = ~ 1 | Tank, data=data, method="ML", na.action=na.omit)
modPB6 <- lme(log(chla) ~ 1 + trophic.level*I(invTi - invTT), random = ~ 1 | Tank, data=data, method="ML", na.action=na.omit)
modPB5 <- lme(log(chla) ~ 1 + I(invTi - invTT) + trophic.level, random = ~ 1 | Tank, data=data, method="ML", na.action=na.omit)
modPB4 <- lme(log(chla) ~ 1 + I(invTi - invTT)*I(invTT - mean(invTT)), random = ~ 1 | Tank, data=data, method="ML", na.action=na.omit)
modPB3 <- lme(log(chla) ~ 1 + I(invTi - invTT) + I(invTT - mean(invTT)), random = ~ 1 | Tank, data=data, method="ML", na.action=na.omit)
modPB2 <- lme(log(chla) ~ 1 + I(invTi - invTT), random = ~ 1 | Tank, data=data, method="ML", na.action=na.omit)
modPB1 <- lme(log(chla) ~ 1 + trophic.level, random = ~ 1 | Tank, data=data, method="ML", na.action=na.omit)
modPB0 <- lme(log(chla) ~ 1, random = ~ 1 | Tank, data=data, method="ML", na.action=na.omit)

PPres <- data.frame(model.sel(modPB0, modPB1, modPB2, modPB3, modPB4, modPB5, modPB6, modPB7, modPB8, modPBF))
```

`r table_nums("Table_S2.1")`

```{r Table_S2.1}
kable(PPres, digits=2, col.names = c('Int','TL','Tw','Tt', 'Tw*Tt', 'Tw*TL','Tt*TL', 'df', 'logLik','AICc','d','w'))
```

```{r}
#### Calculate confidence intervals and model coefficients
modPB <- modPB8 #modPB7

# slope for PB.PP: 
SlPB1 <- fixef(modPB)[5]

# slope for PB.ZP: 
SlPB2 <- fixef(modPB)[5] + fixef(modPB)[8]

# slope for PB.PZN: 
SlPB3 <- fixef(modPB)[5] + fixef(modPB)[9]

# ints for PB.PP: 
IPB1 <- fixef(modPB)[1] - fixef(modPB)[5]*mean(data$invTT)

# ints for PB.ZP: modPB includes all int tPBms, but we leave out the invTi tPBm for among group lines; ints hPBe are at mean(invTT) 
IPB2 <- fixef(modPB)[1] + fixef(modPB)[3] - fixef(modPB)[5]*mean(data$invTT) - fixef(modPB)[8]*mean(data$invTT)

# ints for PB.PZN: 
IPB3 <- fixef(modPB)[1] + fixef(modPB)[4] - fixef(modPB)[5]*mean(data$invTT) - fixef(modPB)[9]*mean(data$invTT)

```

```{r Model estimates for figur 3}
PB.funcP <- function(x) {IPB1 + SlPB1*x} # for trophic level 1
PBvalsP <- PB.funcP(data[(data$trophic.level=="P"),]$invTT)

PB.funcPZ <- function(x) { IPB2 + SlPB2*x } # for trophic level 2
PBvalsPZ <- PB.funcPZ(data[(data$trophic.level=="PZ"),]$invTT)

PB.funcPZN <- function(x) { IPB3 + SlPB3*x } # for trophic level 3
PBvalsPZN <- PB.funcPZN(data[(data$trophic.level=="PZN"),]$invTT)
```

```{r, echo = FALSE}
## calculating confidence intervals for activation energies.
#vcov(modPB) # diagonals of vcov are variances
#vcov(modPB)[1,1] # intercept variance is:

df <- length(data$chla)-(length(coef(modPB))+1)-1
t.stat <- qt(0.975, df = df) #calculates critical t-value for the threshold (first value) and df (= n - p - 1)

# slope for PB.PP: 
#SlPB1 <- fixef(modPB)[5]
#SlPB1.l <- intervals(modPB)$fixed[1]
#SlPB1.u <- intervals(modPB)$fixed[3]
SlPB1.l2 <- SlPB1 - t.stat * sqrt(vcov(modPB)[5,5])
SlPB1.u2 <- SlPB1 + t.stat * sqrt(vcov(modPB)[5,5])

# slope for PB.ZP: 
#SlPB2 <- fixef(modPB)[5] + fixef(modPB)[6]
SlPB2.l <- SlPB2 - t.stat * sqrt(vcov(modPB)[5,5] + vcov(modPB)[8,8] + 2*vcov(modPB)[8,5])
SlPB2.u <- SlPB2 + t.stat * sqrt(vcov(modPB)[5,5] + vcov(modPB)[8,8] + 2*vcov(modPB)[8,5])

# slope for PB.PZN: 
#SlPB3 <- fixef(modPB)[5] + fixef(modPB)[7]
SlPB3.l <- SlPB3 - t.stat * sqrt(vcov(modPB)[5,5] + vcov(modPB)[9,9] + 2*vcov(modPB)[9,5])
SlPB3.u <- SlPB3 + t.stat * sqrt(vcov(modPB)[5,5] + vcov(modPB)[9,9] + 2*vcov(modPB)[9,5])

slopesPB <- (cbind(c(SlPB1, SlPB2, SlPB3), c(SlPB1.l2, SlPB2.l, SlPB3.l), c(SlPB1.u2, SlPB2.u, SlPB3.u)))
rownames(slopesPB) <- c("P", "PZ", "PZN")
colnames(slopesPB) <- c("Ea", "lower", "upper")
```

`r table_nums("Table_S2.2")`

```{r Table S2.2}
kable(slopesPB, digits = 2)
```


```{r}
xlab <- expression(paste('Temperature (',~degree,'C)',sep=''))
PP.plot <- ggplot(data = data, aes(x = -invTi, y = log(chla), ymin = -3, ymax = 3, xmin = -40.2, xmax = -38.2)) +
  theme_bw() +
  theme(legend.position = "none") +
  facet_grid(trophic.level~.) + 
  geom_point(aes(group = as.character(Tankn), color = as.character(Tankn), shape = as.factor(week), alpha = Tankn), size = 2) + 
  theme(panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank(),  
        legend.text = element_text(size = 3), 
        legend.title = element_text(size = 3), 
        legend.key = element_rect(fill = NA), 
        strip.text.y = element_blank(),
        strip.background = element_rect(colour="white", fill="white")) +
  scale_colour_grey(start = 0, end = 0.6, name = "Tank", guide = "none") +
  scale_shape_manual(values = c(1,2,22,23,16,17,8,6)) +
  scale_alpha("Tankn", guide = "none") +
  ylab("ln(ug Chl a / L)") +
  labs(title = "A. Phytoplankton \n Abundance") +
  annotate("text", label = c("i. A", "ii. AG", "iii. AGP"), x = -38.45, y = 2.95) +
  annotate("text", label = c("Ea = 1.30 (0.85, 1.76)", "Ea = 3.15 (2.76, 3.54)", "Ea = 1.65 (1.19, 2.10)"), x = -39.3, y = -2.95, size = 3) +
  scale_x_continuous("Temperature (1/kTi)", sec.axis = sec_axis(~((1/(k*-.))-273), name = xlab))

#PP.plot
```


```{r, fig.width=6, fig.height=3}
####Figure 2ABC: Phytoplankton biomass and how it varied with temperature within tanks (blue lines) and across tanks (black lines).
Fig2ABC <- PP.plot +
  geom_smooth(method = "lm", se = FALSE, inherit.aes = FALSE, aes(x = -invTi, y = log(chla), group = Tank),  size = .8, color = alpha("steelblue", 0.5)) +
 geom_smooth(data = subset(data, trophic.level == "P"), aes(x = -invTT, y = PBvalsP), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'black', size = 1.5) +
 geom_smooth(data = subset(data, trophic.level == "PZ"), aes(x = -invTT, y = PBvalsPZ), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'black', linetype = 1, size = 1.5) +
 geom_smooth(data = subset(data, trophic.level == "PZN"), aes(x = -invTT, y = PBvalsPZN), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'black', linetype = 1, size = 1.5) 

#Fig2ABC
  
#ggsave("Fig2ABC.png", device = "png")
```


#
## 2.2 Net ecosystem oxygen production
```{r, fig.width=3, fig.height=3, echo = FALSE}
data1 <- data[(data$NPP2 >= 0.00001),] #remove 21 negative values 
hist(data1$NPP2)
hist(log(data1$NPP2))

tcp1 <- lme(log(NPP2) ~ 1 + trophic.level, random = ~ 1 | Tank, data=data1, method="ML", na.action=na.omit) 

#summary(tcp1)
#anova(tcp1)
```

```{r, NEP model selection, echo=FALSE}
# NPP candidate model set -------------------------------------------------
modNPPF <- lme(log(NPP2) ~ 1 + I(invTi - invTT) + trophic.level + trophic.level*I(invTi - invTT) + I(invTT - mean(invTT)) + trophic.level*I(invTT - mean(invTT)) + I(invTi - invTT)*I(invTT - mean(invTT)), random = ~ 1 | Tank, data=data1, method="ML", na.action=na.omit)

modNPP8 <- lme(log(NPP2) ~ 1 + trophic.level*I(invTi - invTT) + trophic.level*I(invTT - mean(invTT)), random = ~ 1 | Tank, data=data1, method="ML", na.action=na.omit)

modNPP7 <- lme(log(NPP2) ~ 1 + I(invTi - invTT) + trophic.level + trophic.level*I(invTT - mean(invTT)), random = ~ 1 | Tank, data=data1, method="ML", na.action=na.omit)

modNPP6 <- lme(log(NPP2) ~ 1 + trophic.level*I(invTi - invTT), random = ~ 1 | Tank, data=data1, method="ML", na.action=na.omit)

modNPP5 <- lme(log(NPP2) ~ 1 + I(invTi - invTT) + trophic.level, random = ~ 1 | Tank, data=data1, method="ML", na.action=na.omit)

modNPP4 <- lme(log(NPP2) ~ 1 + I(invTi - invTT)*I(invTT - mean(invTT)), random = ~ 1 | Tank, data=data1, method="ML", na.action=na.omit)

modNPP3 <- lme(log(NPP2) ~ 1 + I(invTi - invTT) + I(invTT - mean(invTT)), random = ~ 1 | Tank, data=data1, method="ML", na.action=na.omit)

modNPP2 <- lme(log(NPP2) ~ 1 + I(invTi - invTT), random = ~ 1 | Tank, data=data1, method="ML", na.action=na.omit)

modNPP1 <- lme(log(NPP2) ~ 1 + trophic.level, random = ~ 1 | Tank, data=data1, method="ML", na.action=na.omit)

modNPP0 <- lme(log(NPP2) ~ 1, random = ~ 1 | Tank, data=data1, method="ML", na.action=na.omit)

#model.sel(modNPP0, modNPP1, modNPP2, modNPP3, modNPP4, modNPP5, modNPP6, modNPP7, modNPP8, modNPPF)

NPres <- data.frame(model.sel(modNPP0, modNPP1, modNPP2, modNPP3, modNPP4, modNPP5, modNPP6, modNPP7, modNPP8, modNPPF))
```

`r table_nums("Table_S2.3")`

```{r Table S2.3}
kable(NPres, digits=2, col.names = c('Int','TL','Tw','Tt', 'Tw*Tt', 'Tw*TL','Tt*TL', 'df', 'logLik','AICc','d','w'))
```

```{r NEP model coefs}
## Average best models: 
m.avgN <- model.avg(modNPP8, modNPPF)
confint(m.avgN) -> ints
coef(m.avgN) -> coefs
#kable(ints, caption = "Table S4: Confidence intervals for averaged models for NPP")

NP.agp <- exp(coefs[1] - coefs[3])
NP.ag <- exp(coefs[1] - coefs[2])
NP.a <- exp(coefs[1])
```

#### NPP Coefficients
```{r}
# slope for NPP.PP: 
Sl1 <- coefficients(m.avgN)[5]

# slope for NPP.ZP: 
Sl2 <- coefficients(m.avgN)[5] + coefficients(m.avgN)[8]
  
# slope for NPP.PZN: 
Sl3 <- coefficients(m.avgN)[5] + coefficients(m.avgN)[9]

# ints for NPP.PP:
I1 <- coefficients(m.avgN)[1] - coefficients(m.avgN)[5]*mean(data1$invTT)

# ints for NPP.ZP: m.avgN includes all int terms, but we leave out the invTi term for among group lines; ints here are at mean(invTT) 
I2 <- coefficients(m.avgN)[1] + coefficients(m.avgN)[2] - coefficients(m.avgN)[5]*mean(data1$invTT) - coefficients(m.avgN)[8]*mean(data1$invTT)

# ints for NPP.PZN: 
I3 <- coefficients(m.avgN)[1] + coefficients(m.avgN)[3] - coefficients(m.avgN)[5]*mean(data1$invTT) - coefficients(m.avgN)[9]*mean(data1$invTT)
```

```{r}
## calculating confidence intervals for activation energies.
#vcov(m.avgN) # diagonals of vcov are variances
#vcov(m.avgN)[1,1] # intercept variance is:

df <- length(data1$NPP2)-(length(coef(m.avgN))+1)-1
t.stat <- qt(0.975, df = df) #calculates critical t-value for the threshold (first value) and df (= n - p - 1)

# slope for N.PP: 
SlN1.l2 <- Sl1 - t.stat * sqrt(vcov(m.avgN)[5,5])
SlN1.u2 <- Sl1 + t.stat * sqrt(vcov(m.avgN)[5,5])

# slope for N.ZP: 
SlN2.l <- Sl2 - t.stat * sqrt(vcov(m.avgN)[5,5] + vcov(m.avgN)[6,6] + 2*vcov(m.avgN)[6,5])
SlN2.u <- Sl2 + t.stat * sqrt(vcov(m.avgN)[5,5] + vcov(m.avgN)[6,6] + 2*vcov(m.avgN)[6,5])

# slope for N.PZN: 
SlN3.l <- Sl3 - t.stat * sqrt(vcov(m.avgN)[5,5] + vcov(m.avgN)[7,7] + 2*vcov(m.avgN)[7,5])
SlN3.u <- Sl3 + t.stat * sqrt(vcov(m.avgN)[5,5] + vcov(m.avgN)[7,7] + 2*vcov(m.avgN)[7,5])

slopesN <- (cbind(c(Sl1, Sl2, Sl3), c(SlN1.l2, SlN2.l, SlN3.l), c(SlN1.u2, SlN2.u, SlN3.u)))
rownames(slopesN) <- c("P", "PZ", "PZN")
colnames(slopesN) <- c("Ea", "lower", "upper")
```

`r table_nums("Table_S2.4")`

```{r Table S2.4}
kable(slopesN, digits = 2)
```

```{r lines for NEP figure}
## estimating coefficients for PLOT 2A: Raw data and fitted lines from the averaged model. Added the predictions of the model to the original dataset (mod.coefsN), then fit lines to those using linear regressions
NPP.funcP <- function(x) { I1 + Sl1*x}
NvalsP <- NPP.funcP(data1[(data1$trophic.level=="P"),]$invTT)

NPP.funcPZ <- function(x) { I2 + Sl2*x }
NvalsPZ <- NPP.funcPZ(data1[(data1$trophic.level=="PZ"),]$invTT)

NPP.funcPZN <- function(x) { I3 + Sl3*x }
NvalsPZN <- NPP.funcPZN(data1[(data1$trophic.level=="PZN"),]$invTT)

```


```{r NPP plot code}
### plotting within- and among-group regressions and model outputs
NPP.plot1 <- ggplot(data = data1, aes(x = -invTi, y = log(NPP2), ymin = -11, ymax = -5)) +
  theme_bw() +
  theme(legend.position = "none") +
  theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank()) +
  theme(strip.background = element_rect(colour="white", fill="white")) +
  theme(strip.text.x = element_blank()) +
  facet_grid(.~trophic.level) + 
  geom_point(aes(group = as.character(Tankn), color = as.character(Tankn), shape = as.factor(week), alpha = Tankn), size = 2) + 
  scale_colour_grey(start = 0, end = 0.6, name = "Tank", guide = "none") +
  scale_alpha("Tankn", guide = "none") +
  scale_x_continuous("", sec.axis = sec_axis(~((1/(k*-.))-273), name = "")) +
  #xlab("") + #Temperature 1/kTi
  ylab("Oxygen Production (NPP) \n ln(umol O2 / L / hr)")

NPP.plot <- ggplot(data = data1, aes(x = -invTi, y = log(NPP2), ymin = -11, ymax = -4, xmin = -40.2, xmax = -38.2)) +
  theme_bw() +
  theme(legend.position = "none",
    panel.grid.minor = element_blank(), 
    panel.grid.major = element_blank(),
    strip.background = element_rect(colour="white", fill="white"),
    strip.text.y = element_blank()) +
  facet_grid(trophic.level~.) + 
  geom_point(aes(group = as.character(Tankn), color = as.character(Tankn), shape = as.factor(week), alpha = Tankn), size = 2) + 
  scale_colour_grey(start = 0, end = 0.6, name = "Tank", guide = "none") +
  scale_alpha("Tankn", guide = "none") +
  #xlab("Temperature 1/kTi") +
  ylab("ln(umol O2 / L / hr)") +
  labs(title = "B. Net Ecosystem \n Production (NEP)") +
  annotate("text", label = c("i. A", "ii. AG", "iii. AGP"), x = -38.45, y =-4.1) +
  annotate("text", label = c("Ea = -1.41 (-2.25, -0.58)", "Ea = -1.21 (-2.56, -0.07)", "Ea = -0.99 (-2.10, 0.12)"), x = -39.3, y = -10.8, size = 3) +
  scale_x_continuous("Temperature (1/kTi)", sec.axis = sec_axis(~((1/(k*-.))-273), name = xlab))
```

```{r}
# Figure 3B ---------------------------------------------------------------
# the within-group lines here are lms fitted to the actual data; I think these should be the modeled data too...
# the among-group lines are model fits based on the best model (so this could be model averaged coefficients too)
Fig2DEF <- 
  NPP.plot + 
  geom_smooth(data = subset(data1), method = "lm", se = FALSE, inherit.aes = FALSE, aes(x = -invTi, y = log(NPP2), group = Tank),  size = .8, color = alpha("steelblue", 0.5)) + 
  geom_smooth(data = subset(data1, trophic.level == "P"), aes(x = -invTT, y = NvalsP), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'black', size = 1.5) +
 geom_smooth(data = subset(data1, trophic.level == "PZ"), aes(x = -invTT, y = NvalsPZ), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'black', size = 1.5) +
  geom_smooth(data = subset(data1, trophic.level == "PZN"), aes(x = -invTT, y = NvalsPZN), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'black', size = 1.5) 
```

```{r, fig.width=6, fig.height=3}
#Fig2DEF
#ggsave("Fig2A.png", device = "png", width = 7, height = 3)
```


##### 2.2 Net ecosystem oxygen consumption (ER)

```{r, Table_2.3, fig.width=3, fig.height=3}
hist(data$ER2)
hist(log(data$ER2))
data2 <- data[(data$ER2 >= 0),] #no values removed
data2 <- data[!is.na(data$ER2),]
```

```{r, echo=FALSE}
## ER candidate model set
modERF <- lme(log(ER2) ~ 1 + I(invTi - invTT) + trophic.level + trophic.level*I(invTi - invTT) + I(invTT - mean(invTT)) + I(invTi - invTT)*I(invTT - mean(invTT)), random = ~ 1 | Tank, data=data2, method="ML", na.action=na.omit) 
modER8 <- lme(log(ER2) ~ 1 + trophic.level*I(invTi - invTT) + trophic.level*I(invTT - mean(invTT)), random = ~ 1 | Tank, data=data2,  method="ML", na.action=na.omit)
modER7 <- lme(log(ER2) ~ 1 + I(invTi - invTT) + trophic.level + trophic.level*I(invTT - mean(invTT)), random = ~ 1 | Tank, data=data2,  method="ML", na.action=na.omit)
modER6 <- lme(log(ER2) ~ 1 + trophic.level*I(invTi - invTT), random = ~ 1 | Tank, data=data2,  method="ML", na.action=na.omit)
modER5 <- lme(log(ER2) ~ 1 + I(invTi - invTT) + trophic.level, random = ~ 1 | Tank, data=data2,  method="ML", na.action=na.omit)
modER4 <- lme(log(ER2) ~ 1 + I(invTi - invTT)*I(invTT - mean(invTT)), random = ~ 1 | Tank, data=data2, method="ML", na.action=na.omit)
modER3 <- lme(log(ER2) ~ 1 + I(invTi - invTT) + I(invTT - mean(invTT)), random = ~ 1 | Tank, data=data2, method="ML", na.action=na.omit)
modER2 <- lme(log(ER2) ~ 1 + I(invTi - invTT), random = ~ 1 | Tank, data=data2, method="ML", na.action=na.omit)
modER1 <- lme(log(ER2) ~ 1 + trophic.level, random = ~ 1 | Tank, data=data2, method="ML", na.action=na.omit)
modER0 <- lme(log(ER2) ~ 1, random = ~ 1 | Tank, data=data2, method="ML", na.action=na.omit)

#model.sel(modER0, modER1, modER2, modER3, modER4, modER5, modER6, modER7, modER8, modERF)

ERres <- data.frame(model.sel(modER0, modER1, modER2, modER3, modER4, modER5, modER6, modER7, modER8, modERF))
```

`r table_nums("Table_S2.5")`

```{r Table S5}
kable(ERres, digits=2, col.names = c('Int','TL','Tw','Tt', 'Tw*Tt', 'Tw*TL','Tt*TL', 'df', 'logLik','AICc','d','w'))
```

## ER coefficients

```{r}
modER <- modER7

ERints <- intervals(modER, which = "fixed")
ER.agp <- exp(ERints$fixed[1,2] - ERints$fixed[4,2])
ER.ag <- exp(ERints$fixed[1,2] - ERints$fixed[3,2])
ER.a <- exp(ERints$fixed[1,2])

# slope for ER.PP: 
SlER1 <- fixef(modER)[5]

# slope for ER.ZP: 
SlER2 <- fixef(modER)[5] + fixef(modER)[6]

# slope for ER.PZN: 
SlER3 <- fixef(modER)[5] + fixef(modER)[7]

# ints for ER.PP: 
IER1 <- fixef(modER)[1] - fixef(modER)[5]*mean(data2$invTT)

# ints for ER.ZP: modER includes all int terms, but we leave out the invTi term for among group lines; ints here are at mean(invTT) 
IER2 <- fixef(modER)[1] + fixef(modER)[3] - fixef(modER)[5]*mean(data2$invTT) - fixef(modER)[6]*mean(data2$invTT)

# ints for ER.PZN: 
IER3 <- fixef(modER)[1] + fixef(modER)[4] - fixef(modER)[5]*mean(data2$invTT) - fixef(modER)[7]*mean(data2$invTT)

ER.funcP <- function(x) {IER1 + SlER1*x} # for trophic level 1
RvalsP <- ER.funcP(data2[(data2$trophic.level=="P"),]$invTT)

ER.funcPZ <- function(x) { IER2 + SlER2*x } # for trophic level 2
RvalsPZ <- ER.funcPZ(data2[(data2$trophic.level=="PZ"),]$invTT)

ER.funcPZN <- function(x) { IER3 + SlER3*x } # for trophic level 3
RvalsPZN <- ER.funcPZN(data2[(data2$trophic.level=="PZN"),]$invTT)
```

```{r}
## calculating confidence intervals for activation energies.
#vcov(modER) # diagonals of vcov are variances
#vcov(modER)[1,1] # intercept variance is:

df <- length(data$ER2)-(length(coef(modER))+1)-1
t.stat <- qt(0.975, df = df) #calculates critical t-value for the threshold (first value) and df (= n - p - 1)

# slope for ER.PP: 
SlER1.l2 <- SlER1 - t.stat * sqrt(vcov(modER)[5,5])
SlER1.u2 <- SlER1 + t.stat * sqrt(vcov(modER)[5,5])

# slope for ER.ZP: 
SlER2.l <- SlER2 - t.stat * sqrt(vcov(modER)[5,5] + vcov(modER)[6,6] + 2*vcov(modER)[6,5])
SlER2.u <- SlER2 + t.stat * sqrt(vcov(modER)[5,5] + vcov(modER)[6,6] + 2*vcov(modER)[6,5])

# slope for ER.PZN: 
SlER3.l <- SlER3 - t.stat * sqrt(vcov(modER)[5,5] + vcov(modER)[7,7] + 2*vcov(modER)[7,5])
SlER3.u <- SlER3 + t.stat * sqrt(vcov(modER)[5,5] + vcov(modER)[7,7] + 2*vcov(modER)[7,5])

slopesER <- (cbind(c(SlER1, SlER2, SlER3), c(SlER1.l2, SlER2.l, SlER3.l), c(SlER1.u2, SlER2.u, SlER3.u)))
rownames(slopesER) <- c("P", "PZ", "PZN")
colnames(slopesER) <- c("Ea", "lower", "upper")
```

`r table_nums("Table_S2.6")`

```{r Table_S7}
kable(slopesER)
```


```{r ER plot}
ER.plot <- ggplot(data = data2, aes(x = -invTi, y = log(ER2), ymin = -8, ymax = -4, xmin = -40.2, xmax = -38.2)) + 
  theme_bw() +
  theme(legend.position = "none",
        panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank(),
        strip.background = element_blank(), 
        strip.text.y = element_blank()) +
  facet_grid(trophic.level~.) + 
  geom_point(aes(group = as.character(Tankn), color = as.character(Tankn), shape = as.factor(week), alpha = Tankn), size = 2) + 
  scale_colour_grey(start = 0, end = 0.6, name = "Tank", guide = "none") +
  scale_alpha("Tankn", guide = "none") +
  scale_shape(name = "Week", guide = guide_legend(ncol = 2)) +
  xlab("Temperature (1/kTi)") +
  ylab("ln(umol O2 / L / hr)") +
  labs(title = "C. Net Ecosystem \n Respiration (ER)") +
  annotate("text", label = c("i. A", "ii. AG", "iii. AGP"), x = -38.45, y = -4.1) + 
  annotate("text", label = c("Ea = -1.32 (-1.85, -0.79)", "Ea = -0.88 (-1.32, -0.43)", "Ea = -0.33 (-0.86, 0.20)"), x = -39.3, y = -7.8, size = 3) +
  scale_x_continuous("Temperature (1/kTi)", sec.axis = sec_axis(~((1/(k*-.))-273), name = xlab))
  
```

```{r, fig.width=6, fig.height=3}
Fig2GHI <- 
ER.plot +
  geom_smooth(method = "lm", se = FALSE, inherit.aes = FALSE, aes(x = -invTi, y = log(ER2), group = Tank),  size = .8, color = alpha("steelblue", 0.5)) +
  geom_smooth(data = subset(data2, trophic.level == "P"), aes(x = -invTT, y = RvalsP), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'black', size = 1.5) +
  geom_smooth(data = subset(data2, trophic.level == "PZ"), aes(x = -invTT, y = RvalsPZ), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'black', linetype = 1, size = 1.5) +
  geom_smooth(data = subset(data2, trophic.level == "PZN"), aes(x = -invTT, y = RvalsPZN), method = "lm", se = FALSE, inherit.aes = FALSE, formula = y ~ x, color = 'black', linetype = 1, size = 1.5) 

#Fig2GHI
```

##### Figure 3 (Full)
```{r, fig.width=7, fig.height=7}

multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  plots <- c(list(...), plotlist)
  
  numPlots = length(plots)
  
  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                     ncol = cols, nrow = ceiling(numPlots/cols))
  }
  
  if (numPlots==1) {
    print(plots[[1]])
    
  } else {
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
    
    for (i in 1:numPlots) {
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
      
      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```

`r fig_nums("Fig_S2.3")`

```{r Fig_2.3}
multiplot(Fig2ABC, Fig2DEF, Fig2GHI, cols = 3)
```

```{r}
png('Figure3.png', width = 7, height = 7, units = 'in', res = 300)
multiplot(Fig2ABC, Fig2DEF, Fig2GHI, cols = 3)
dev.off()
```


